Copyright

### 2025-02-10 copyright.qmd
Minor improvements
- Decrease size of penguins image
- Detailed instructions for creating a text file

```{.md .code-overflow-wrap}
!["[Chinstrap Penguin](https://flic.kr/p/2pEKnUr)" by "steve b" licensed under [CC0 1.0](https://creativecommons.org/publicdomain/zero/1.0/)](penguin.jpg)
```

@@

```{.md .code-overflow-wrap}
!["[Chinstrap Penguin](https://flic.kr/p/2pEKnUr)" by "steve b" available under [CC0 1.0](https://creativecommons.org/publicdomain/zero/1.0/) from [`flic.kr/p/2pEKnUr`](https://flic.kr/p/2pEKnUr)](penguin.jpg)
```
:::

@@

In addition, we recommend creating a file called `LICENSE.txt`
to describe the license of the image:

>>>>

```{.md .code-overflow-wrap}
!["[Chinstrap Penguin](https://flic.kr/p/2pEKnUr)" by "steve b" licensed under [CC0 1.0](https://creativecommons.org/publicdomain/zero/1.0/)](penguin.jpg){width=50%}
```

@@

```{.md .code-overflow-wrap}
!["[Chinstrap Penguin](https://flic.kr/p/2pEKnUr)" by "steve b" available under [CC0 1.0](https://creativecommons.org/publicdomain/zero/1.0/) from [`flic.kr/p/2pEKnUr`](https://flic.kr/p/2pEKnUr)](penguin.jpg){width=50%}
```
:::

@@

In addition, we recommend creating a file called `LICENSE.txt`
to describe the license of the image.
Click on _File_ > _New File_ > _Text File_,
then on _File_ > _Save_, and choose `LICENSE.txt` as filename.
